---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bikr

<!-- badges: start -->
<!-- badges: end -->

The goal of bikr is to present statistical analysis functionality for a sample BikeShare Dataset for the city of Pittsburgh, PA, retrieved from [](). This dataset presents trip data for ___ BikeShare rides during the period ____. The bikr package provides high-level analysis capabilities for BikeShare trip data, to compare trip lengths, time durations, as well as trip characteristics by rider characteristics. 
A number of additional data visualization components are also available, including scatterplots, histograms and line charts.

## Installation

You can install the most recent version of bikr via:

``` r
if(!require(remotes)){
    install.packages("remotes")
    library(remotes)
}
remotes::install_github("vanveghd/bikr")
```

## Example

Various functions are available in the bikr package for data visualization, statistical analysis and cross-referencing.
The code below is one function, which gives visual presentations of BikeShare trip distances (histograms, length by date, etc.)

```{r example}
library(bikr)
## basic example code

bikr::visualize_route_durations()
```

## Functions available in first version of bikr

compare_means()
visualize_route_durations()

## References

_To access/download the initial dataset from Pittsburgh BikeShare:_  
[https://www.kaggle.com/adamscarroll/pittsburgh-healthy-ride-bikeshare-rentals-2021-q1](https://www.kaggle.com/adamscarroll/pittsburgh-healthy-ride-bikeshare-rentals-2021-q1)
