---
title: "bikr-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bikr-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# The bikr bikeshare analysis package
### (C) Daniel Van Veghel, _McMaster University, 2021_
***

The bikr package is a standalone R package used for the analysis and visualization of BikeShareData. 
The first version of the package includes a sample bikeshare route dataset from Pittsburgh, Pennsylvania. 
Several functions are included in the package; these will be shown in detail in the coming code chunks. 

**The bikr package is available on the author's [Github Repository](http://www.github.com/vanveghd/bikr)**

```{r setup}
# After installing the bikr package from the Github Repository
library(bikr)
```

### **The Data:**

The data is available for download from the Google Datasets Search Engine, and was made publicly available by **Adam S. Carroll**. The data details individual trips for all bikeshare rides in Pittsburgh, for the first Quarter of 2021 (approximately 14,000 rides).

While documentation about each variable in the dataset is available via:

```{r}
?bikr
```

Below are the variables and a brief outline of each of them:
- **trip.id:** ID Number for the individual trip
- **Starttime:** The date/time the bikeshare trip began
- **Stoptime:** The date/time the bikeshare trip ended
- **Bikeid:** The BikeShare bike's identifier number
- **Tripduration:** The length of the trip in minutes
- **From.station.id:** The origin hub ID number
- **From.station.name:** The origin hub name/location
- **To.station.id:** The destination hub ID number
- **To.station.name:** The destination hub name/location
- **Usertype:** Whether the rider is a customer or subscriber

### **The functions:**

- compare_means( _mean1, mean2, var1, var2, n1, n2_ ): a two-sample t-test for comparing the differences in means.  The function produces two values -- 1) the t-value from the t-distribution, of the difference in means and 2) the associated probability from the distribution for this specific t-value. 

- visualize_trip_durations(): presents data visualizations of the Tripduration variable in the BikeShare dataset. There are no parameters. The function produces a histogram, boxplot and barplot to compare the means of different subgroups (based on the Usertype column in the dataset).

#### **Example:**

```{r}
# For example:
bikr::compare_means(25, 30, 28, 40, 33, 34)

```

Later versions of this package are likely to include more functions with better analytical capabilities for the bikeshare data. 
